The development of infants' responses to mispronunciations - A Meta-Analysis

### 2018-11-26 Paper_Analyses.tex
Next round of comments
Updated data, added papers where we could not compute ES, added outlier exclusion info

@@

{[}Christina: changed concepts to mechanisms in the next paragraph,
because I want to refer to what they represent, but I am not sure it's
the right term{]}{[}Katie: Karen (Mulak) talks about these terms as
concepts. Mechanisms to me means some sort of internalization, that they
would have had this ability all along and just need to apply it. It
could be that we fundamentally disagree on this, but to me these are
things that infants discover. Later on we use principles. What about
\enquote{principles that infants must discover}\ldots{} \enquote{in
order to form adult-like word representations}? I took away
\enquote{which are both present in the mature language processing
system}.{]}

@@

{[}Katie: since we actually don't have theoretical framework support for
the no-change theory, I've changed around the sentence below to
explicitly say that only 2 of the 3 are predicted by theoretical
accounts.{]}

@@

We first generated a list of potentially relevant items to be included
in our meta-analysis by creating an expert list. This process yielded
110 items. We then used the google scholar search engine to search for
papers citing the original Swingley \& Aslin (2000) publication. This
search was conducted on 22 September, 2017 and yielded 288 results. We
screened the resulting 398 items, removing 99 duplicate items. We
screened remaining 299 items for their title and abstract to determine
whether it met the following inclusion criteria: (1) original data was
reported; (2) the experiment examined familiar word recognition and
mispronunciations; (3) infants studied were under 31-months-of-age; (4)
the dependent variable was derived from proportion of looks to a target
image versus a distractor in a eye movement experiment; (5) the stimuli
were auditory speech. The final sample (n = \emph{32}) consisted of 27
journal articles, 1 proceedings paper, 2 thesis, and 2 unpublished
reports. We will refer to these items collectively as papers. Table 1
(Summary Table) provides an overview of all papers included in the
present meta-analysis.

@@

The 32 papers we identified as relevant were then coded with as much
consistently reported detail as possible (Tsuji, Bergmann, \& Cristia,
2014; Bergmann et al., 2018). For each experiment (note that a paper
typically has multiple experiments), we entered variables describing the
publication, population, experiment design and stimuli, and results. For
the analyses presented in this section, we focus on the following
characteristics:

@@

We separated conditions according to whether or not the target word was
mispronounced to be able to investigate infants' looking to the target
picture as well as their mispronunciation sensitivity, which is the
difference between looks to the target in correct and mispronounced
trials. When the same infants were further exposed to multiple
mispronunciation conditions and the results were reported separately in
the paper, we also entered each condition as a separate row (e.g.,
consonant versus vowel mispronunciations; Mani \& Plunkett, 2007). The
fact that the same infants contributed data to multiple rows (minimally
those containing information on correct and mispronounced trials) leads
to shared variance across effect sizes, which we account for in our
analyses (see next section). We will call each row a record; in total
there were 251 records in our data.

@@

{[}Christina{]} I think it would be useful to say how many records, not
papers, report each measure. e.g. \enquote{(n = xxx records from yyy
papers)}. Would that be ok? {[}Katie{]} Totally! I think that gives a
good bit of information. Good suggestion!

@@

{[}Christina{]} Katie, do you know whether the difference is computed
based on items, participants, trials\ldots{}? Is there consistency?
{[}Katie{]} From working with Nivi, we did it participants x condition
or participants x trial (but mostly the former). But, this is not
something we reported in papers. I don't think I read it at all when
putting together the dataset for this either.

@@

{[}Christina{]} These numbers seem wrong! Again, how about (xx effect
sizes from yy papers)? {[}Katie{]} Well, they are kind of wrong :) Two
papers report both for different experimental conditions. I've given the
explanation now, not sure if that is good enough, but I'm really not
sure how to say it a different way. {[}Katie{]} Do you want number of
records and papers for the imputed correlations as well? You've put a
-1, assuming there was something wrong with one of the papers or
something like that? How does that shake out for number of records?

We calculated Hedges' \emph{g} using the raw means and standard
deviations reported in the paper (\emph{n} = 177 records from 25 papers)
or using reported t-values (\emph{n} = 74 records from 9 papers). Two
papers reported raw means and standard deviations for some experimental
conditions and just t-values for the remaining experimental conditions
(Swingley, 2016; Altvater-Mackensen et al., 2014). Raw means and
standard deviations were extracted from figures for 3 papers. In a
within-participation design, when two means are compared (i.e.~looking
during pre- and post-naming) it is necessary to obtain correlations
between the two measurements at the participant level to calculate
effect sizes and effect size variance based on t-values. Upon request we
were provided with correlation values for one paper (Altvater-Mackensen,
2010); we were able to compute correlations using means, standard
deviations, and t-values for \emph{n} = 4 (following Csibra, et al.
2016, Appendix B; see also Rabagliati, Ferguson, \& Lew-Williams, 2018).
Correlations were imputed for the remaining papers (see Black \&
Bergmann, 2017, for the same procedure). We could compute a total of 104
effect sizes for correct pronunciations and 147 for mispronunciations.

@@

Second, we analyze all of the significant results in the dataset using a
p-curve from the p-curve app (v4.0, p-curve.com; @pcurve). This p-curve
tests for evidential value by examining whether the p-values follow the
expected distribution of a right skew in case the alternative hypothesis
is true, versus a flat distribution that speaks for no effect being
present in the population and all significant effect being spurious.
Responses to correctly pronounced and mispronounced labels are predicted
to show different patterns of looking behavior. In other words, there is
an expectation that infants should look to the target when hearing a
correct pronunciation, but some studies may report either significant
looks or no significant looks to the target when hearing a mispronounced
label

{[}Christina{]} Katie, is that right, can you add a citation?
{[}Katie{]} I've rewritten it a bit to be explicit about the difference
between expectations for correct and mispronounced labels. I'm not sure
what to cite though. The papers that find significant looks or no
significant looks? That's basically the meta-analysis. Or some citation
that talks about what looking to the target upon hearing a
mispronunciation means in comparison to what target looks being
decreased for mispronunciations relative to correct pronunciations
means? I'm not so sure whether anyone has actually talked about that
difference before, not sure what to cite.

(i.e.~there might be no effect present in the population, see e.g., );
as a result, we conduct these two analyses to assess publication bias
separately for both conditions.

@@

@@

Of the 32 papers included in the meta-analysis, 13 analyzed the
relationship between vocabulary scores and object recognition for
correct pronunciations and mispronunciations (comprehension = 11 papers
and 43 records; production = 2 papers and 16 records). There is reason
to believe that production data are different from comprehension data
(the former being easier to estimate for parents in the typical
questionnaire-based assessment; Kidd citation), and we therefore planned
to analyze these two types of vocabulary measurement separately.
However, only 2 papers reported correlations with productive vocabulary
scores, limiting the conclusions that can be drawn. In our vocabulary
analysis, we therefore focus exclusively on the relationship between
comprehension and mispronunciation sensitivity.

@@

We first considered the relationship between vocabulary and object
recognition for correct pronunciations. Higher comprehension scores were
associated with greater object recognition in response to correct
pronunciations for 9 of 12 experimental conditions, with correlation
values ranging from -0.17 to 0.48. The mean effect size Pearson's
\emph{r} of 0.09 was small and did not differ significantly from zero
(CI {[}-0.01; 0.19{]} \emph{p} = 0.079). However, the lower bound of the
CI is close to zero, and one might hypothesize that with more power the
small relationship might become significant. At the same time, a larger
sample might confirm our conclusion that there is no relationship. As a
result, we can not draw firm conclusions about the relationship between
comprehension scores and object recognition in response to correct
pronunciations.

We next considered the relationship between vocabulary and object
recognition for mispronunciations. Higher comprehension scores were
associated with greater object recognition in response to correct
pronunciations for 17 of 31 experimental conditions, with correlation
values ranging from -0.35 to 0.57. The mean effect size Pearson's
\emph{r} of 0.04 was small and did not differ significantly from zero
(CI {[}-0.03; 0.10{]} \emph{p} = 0.246). Similar to the relationship
between comprehension scores and correct pronunciation object
identification, the small correlations and large variances suggest a
lack of relationship between vocabulary and object recognition for
mispronunciations. We again emphasize that we cannot draw firm
conclusions due to the small number of studies we were able to include
here.

@@

{[}Christina{]} This section talked about several variables in 2
categories, but in reality there are only 2 variables, right? I am not
100\% sure about total trial length as being the first or being
mentioned at all, might it be better to focus on time window analyzed
and then say \enquote{Oh, btw, total trial length totally does nothing
so we don't have to discuss it further} I am not sure, so feel free to
re-rewrite this, but now it better lines up with everything before
because trial length kinda comes out of nowhere. {[}Katie{]} That's
fair! I think maybe we don't need the full analysis for total time
presented or for the offset analysis, but I'd like to still mention them
because it really shows that its something about this post-naming time
window choice that influences it, and not just fishing around for
variability until we find something that works. In the end there are 2
interesting analyses, but offset could have been interesting (but
wasn't). Therefore, I'd still like to refer to the timing variables as a
type of category. Otherwise, we say we'll do size of time window
analyzed, but then we have information about other timing stuff as well.

@@

We next examined whether the type of dependent variable calculated
modulated the development of mispronunciation sensitivity. When age was
included as an additional moderator, the moderator test was significant
QM(11) = 273.585, \emph{p}\textless{} .001. The estimate for the
interaction between Pre vs.~Post, condition, and age was significantly
smaller than that of the Post dependent variable (\(\beta\) = -0.089, SE
= 0.03, 95\% CI{[}-0.148, -0.03{]}, \emph{p}= 0.003), but the difference
between the Difference Score and Post in the interaction with condition
and age was small and not significant (\(\beta\) = -0.036, SE = 0.027,
95\% CI{[}-0.088, 0.016{]}, \emph{p}= 0.174). This relationship is
plotted in Figure 4b. When the dependent variable was Pre vs.~Post,
mispronunciation sensitivity decreased with infant age, while in
comparison, when the dependent variable was Post, mispronunciation
sensitivity increased with infant age. There was no difference in
mispronunciation sensitivity change with infant development between the
Post and Difference Score dependent variables.

>>>>

{[}Christina: Big change: I just realized that we also need to report
where we could not compute effect sizes, added this info. {]}

@@

{[}Christina: changed concepts to mechanisms in the next paragraph,
because I want to refer to what they represent, but I am not sure it's
the right term{]}{[}Katie: Karen (Mulak) talks about these terms as
concepts. Mechanisms to me means some sort of internalization, that they
would have had this ability all along and just need to apply it. It
could be that we fundamentally disagree on this, but to me these are
things that infants discover. Later on we use principles. What about
\enquote{principles that infants must discover}\ldots{} \enquote{in
order to form adult-like word representations}? I took away
\enquote{which are both present in the mature language processing
system}.{]} {[}Christina: I like principles. This is then good for
me.{]}

@@

{[}Katie: since we actually don't have theoretical framework support for
the no-change theory, I've changed around the sentence below to
explicitly say that only 2 of the 3 are predicted by theoretical
accounts.{]}{[}Christina: Works for me. I am just thinking what the
Vihman-style framework says. do you happen to know? I think the Renner
thesis discusses it.{]}

@@

{[}Christina: OK to age. Apa table works for me, weird. It should come
with papaja. Might be related to the issues you have wrt to citations?
{]}{[}Christina: Suggestions re: table. Add N effect sizes? you cna do
it with summarise(number\_ES = n()) I think{]} {[}Christina: Btw, I
think I've corrected short\_cite in the online spreadsheet, so the table
should be fine now.{]}

We first generated a list of potentially relevant items to be included
in our meta-analysis by creating an expert list. This process yielded
110 items. We then used the google scholar search engine to search for
papers citing the original Swingley \& Aslin (2000) publication. This
search was conducted on 22 September, 2017 and yielded 288 results. We
removed 99 duplicate items and screened the remaining 299 items for
their title and abstract to determine whether each met the following
inclusion criteria: (1) original data was reported; (2) the experiment
examined familiar word recognition and mispronunciations; (3) infants
studied were under 31-months-of-age and typically developing; (4) the
dependent variable was derived from proportion of looks to a target
image versus a distractor in a eye movement experiment; (5) the stimuli
were auditory speech. The final sample (n = \emph{34}) consisted of 28
journal articles, 1 proceedings paper, 3 thesis, and 2 unpublished
reports. We will refer to these items collectively as papers. Table 1
(Summary Table) provides an overview of all papers included in the
present meta-analysis.

@@

The 34 papers we identified as relevant were then coded with as much
consistently reported detail as possible (Tsuji, Bergmann, \& Cristia,
2014; Bergmann et al., 2018). For each experiment (note that a paper
typically has multiple experiments), we entered variables describing the
publication, population, experiment design and stimuli, and results. For
the analyses presented in this section, we focus on the following
characteristics:

@@

We separated conditions according to whether or not the target word was
mispronounced to be able to investigate infants' looking to the target
picture as well as their mispronunciation sensitivity, which is the
difference between looks to the target in correct and mispronounced
trials. When the same infants were further exposed to multiple
mispronunciation conditions and the results were reported separately in
the paper, we also entered each condition as a separate row (e.g.,
consonant versus vowel mispronunciations; Mani \& Plunkett, 2007). The
fact that the same infants contributed data to multiple rows (minimally
those containing information on correct and mispronounced trials) leads
to shared variance across effect sizes, which we account for in our
analyses (see next section). We will call each row a record; in total
there were 271 records in our data.

@@

{[}Christina: I needed to move this around because we first need to say
that we could not compute some effect sizes and removed outlierts.{]}

{[}Christina{]} These numbers seem wrong! Again, how about (xx effect
sizes from yy papers)? {[}Katie{]} Well, they are kind of wrong :) Two
papers report both for different experimental conditions. I've given the
explanation now, not sure if that is good enough, but I'm really not
sure how to say it a different way. {[}Katie{]} Do you want number of
records and papers for the imputed correlations as well? You've put a
-1, assuming there was something wrong with one of the papers or
something like that? How does that shake out for number of records?
{[}Christina: No clue what the -1 was, sorry.{]}

We calculate Hedges' \emph{g} using the raw means and standard
deviations reported in the paper (\emph{n} = 186 records from 26 papers)
or using reported t-values (\emph{n} = 74 records from 9 papers). Two
papers reported raw means and standard deviations for some experimental
conditions and just t-values for the remaining experimental conditions
(Swingley, 2016; Altvater-Mackensen et al., 2014). Raw means and
standard deviations were extracted from figures for 4 papers. In a
within-participation design, when two means are compared (i.e.~looking
during pre- and post-naming) it is necessary to obtain correlations
between the two measurements at the participant level to calculate
effect sizes and effect size variance based on t-values. Upon request we
were provided with correlation values for one paper (Altvater-Mackensen,
2010); we were able to compute correlations using means, standard
deviations, and t-values for \emph{n} = 5 (following Csibra, et al.
2016, Appendix B; see also Rabagliati, Ferguson, \& Lew-Williams, 2018).
Correlations were imputed for the remaining papers (see Black \&
Bergmann, 2017, for the same procedure). For two papers, we could not
derive any effect size (Ballem \& Plunkett, Renner), and for a third
paper, we do not have sufficient information in one record to compute
effect sizes (Skoruppa). We compute a total of 106 effect sizes for
correct pronunciations and 150 for mispronunciations. Following standard
meta-analytic practice, we remove outliers, i.e.~effect sizes more than
3 standard deviations from the respective mean effect size. This leads
to the exclusion of 2 records for correct pronunciations and 3 records
for mispronunciations.

{[}Christina: In the above 2 paragraphs I got confused, should it be
present or past. I think it switched in the las tparagraph so I started
to adapt, but I think it would be best for you to decide. {]}

@@

@@

@@

Second, we analyze all of the significant results in the dataset using a
p-curve from the p-curve app (v4.0, p-curve.com; @pcurve). This p-curve
tests for evidential value by examining whether the p-values follow the
expected distribution of a right skew in case the alternative hypothesis
is true, versus a flat distribution that speaks for no effect being
present in the population and all observed significant effects being
spurious. Responses to correctly pronounced and mispronounced labels are
predicted to show different patterns of looking behavior. In other
words, there is an expectation that infants should look to the target
when hearing a correct pronunciation, but studies vary in their report
of significant looks to the target when hearing a mispronounced label
(i.e.~there might be no effect present in the population, see e.g., );
as a result, we conduct these two analyses to assess publication bias
separately for both conditions.

@@

{[}Chrisitna: If you add prisma, then this is figure 2{]}

@@

Of the 32 papers included in the meta-analysis, 13 analyzed the
relationship between vocabulary scores and object recognition for
correct pronunciations and mispronunciations (comprehension = 11 papers
and 39 records; production = 3 papers and 20 records). There is reason
to believe that production data are different from comprehension data
(the former being easier to estimate for parents in the typical
questionnaire-based assessment; Kidd citation), and we therefore planned
to analyze these two types of vocabulary measurement separately.
However, only 3 papers reported correlations with productive vocabulary
scores, limiting the conclusions that can be drawn. In our vocabulary
analysis, we therefore focus exclusively on the relationship between
comprehension and mispronunciation sensitivity.

@@

We first considered the relationship between vocabulary and object
recognition for correct pronunciations. Higher comprehension scores were
associated with greater object recognition in response to correct
pronunciations for 9 of 10 experimental conditions, with correlation
values ranging from -0.16 to 0.48. The mean effect size Pearson's
\emph{r} of 0.14 was small and did not differ significantly from zero
(CI {[}0.03; 0.25{]} \emph{p} = 0.012). However, the lower bound of the
CI is close to zero, and one might hypothesize that with more power the
small relationship might become significant. At the same time, a larger
sample might confirm our conclusion that there is no relationship. As a
result, we can not draw firm conclusions about the relationship between
comprehension scores and object recognition in response to correct
pronunciations.

We next considered the relationship between vocabulary and object
recognition for mispronunciations. Higher comprehension scores were
associated with greater object recognition in response to correct
pronunciations for 17 of 29 experimental conditions, with correlation
values ranging from -0.35 to 0.57. The mean effect size Pearson's
\emph{r} of 0.05 was small and did not differ significantly from zero
(CI {[}-0.01; 0.12{]} \emph{p} = 0.119). Similar to the relationship
between comprehension scores and correct pronunciation object
identification, the small correlations and large variances suggest a
lack of relationship between vocabulary and object recognition for
mispronunciations. We again emphasize that we cannot draw firm
conclusions due to the small number of studies we were able to include
here.

@@

{[}Christina{]} This section talked about several variables in 2
categories, but in reality there are only 2 variables, right? I am not
100\% sure about total trial length as being the first or being
mentioned at all, might it be better to focus on time window analyzed
and then say \enquote{Oh, btw, total trial length totally does nothing
so we don't have to discuss it further} I am not sure, so feel free to
re-rewrite this, but now it better lines up with everything before
because trial length kinda comes out of nowhere. {[}Katie{]} That's
fair! I think we don't need the full analysis for total time presented,
but I'd like to still mention all of them because it really shows that
its something about this post-naming time window choice that influences
it, and not just fishing around for variability until we find something
that works. In the end there are 2 interesting analyses, but offset
could have been interesting (but wasn't). Therefore, I'd still like to
refer to the timing variables as a type of category. Otherwise, we say
we'll do size of time window analyzed, but then we have information
about other timing stuff as well.

@@

We next examined whether the type of dependent variable calculated
modulated the development of mispronunciation sensitivity. When age was
included as an additional moderator, the moderator test was significant
QM(11) = 273.585, \emph{p}\textless{} .001. The estimate for the
interaction between Pre vs.~Post, condition, and age was significantly
smaller than that of the Post dependent variable (\(\beta\) = -0.089, SE
= 0.03, 95\% CI{[}-0.148, -0.03{]}, \emph{p}= 0.003), but the difference
between the Difference Score and Post in the interaction with condition
and age was small and not significant (\(\beta\) = -0.036, SE = 0.027,
95\% CI{[}-0.088, 0.016{]}, \emph{p}= 0.174). This relationship is
plotted in Figure 4b. When the dependent variable was Pre vs.~Post,
mispronunciation sensitivity decreased with infant age, while in
comparison, when the dependent variable was Post, mispronunciation
sensitivity increased with infant age. There was no difference in
mispronunciation sensitivity change with infant development between the
Post and Difference Score dependent variables. Similar to size of
post-naming time window analyzed, all three possible developmental
hypotheses might be supported depending on the dependent variable
reported. In other words, choice of dependent variable may influence the
conclusion drawn regarding how mispronunciation sensitivity may change
with infant age.
